Random Forests, LAs

### 2024-08-16 src/la_RF_corrected.Rmd
all but OA

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4718, 4690, 5040, 4718, 5055, 4704, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE        Rsquared   MAE        
#   2     variance    0.01366816  0.8895425  0.009767759
#   2     extratrees  0.01350182  0.8900993  0.009603882
#   4     variance    0.01408821  0.8841051  0.010134321
#   4     extratrees  0.01354075  0.8914524  0.009664646
#   6     variance    0.01445541  0.8772260  0.010417962
#   6     extratrees  0.01369444  0.8897055  0.009772824
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees
#  and min.node.size = 5.

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_LA_corrected.png")
ggplot(varimp_mars) + theme_minimal() + labs(x="") #+ theme(panel.background = element_rect(fill = "white"))
ggsave(path.out)
```

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4044, 3685, 4032, 4044, 4044, 3696, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.2182933  0.5361604  0.1560099
#   2     extratrees  0.2099702  0.5660477  0.1501194
#   4     variance    0.2168118  0.5238461  0.1550630
#   4     extratrees  0.2074722  0.5590058  0.1489474
#   6     variance    0.2268891  0.5014882  0.1631466
#   6     extratrees  0.2082266  0.5503986  0.1490911
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 4, splitrule = extratrees
#  and min.node.size = 5.

>>>>

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4718, 4690, 5040, 4718, 5055, 4704, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE        Rsquared   MAE       
#   2     variance    0.02811777  0.8509273  0.01912432
#   2     extratrees  0.02782836  0.8508316  0.01901921
#   4     variance    0.02867344  0.8466191  0.01970102
#   4     extratrees  0.02795250  0.8509000  0.01911956
#   6     variance    0.02974784  0.8364575  0.02066007
#   6     extratrees  0.02830277  0.8482189  0.01944133
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees and min.node.size = 5.

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_LA_corrected.png")
ggplot(varimp_mars) + theme_minimal() + labs(x="") #+ theme(panel.background = element_rect(fill = "white"))
ggsave(path.out)

path.out <- paste0(path, "/outputs/rf/figures/varimp_LA_corrected.csv")
varimp_mars$importance %>% 
  rownames_to_column() %>%
  rename(variable = rowname,
         importance = Overall) %>% 
  write_csv(path.out)
```

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4044, 3685, 4032, 4044, 4044, 3696, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.2658416  0.5284505  0.1934243
#   2     extratrees  0.2612133  0.5292689  0.1900297
#   4     variance    0.2621564  0.5194092  0.1912807
#   4     extratrees  0.2611575  0.5183202  0.1910029
#   6     variance    0.2609983  0.5140347  0.1891971
#   6     extratrees  0.2607463  0.5124544  0.1907650
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 6, splitrule = extratrees and min.node.size = 5.

### 2024-08-16 src/la_RF_corrected_10.Rmd
all but OA

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4718, 4690, 5040, 4718, 5055, 4704, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.1881989  0.7750790  0.1223893
#   2     extratrees  0.1944376  0.7543149  0.1274344
#   4     variance    0.1906884  0.7730657  0.1256452
#   4     extratrees  0.1930998  0.7596818  0.1276155
#   6     variance    0.1937399  0.7677967  0.1282843
#   6     extratrees  0.1927437  0.7608415  0.1277447
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = variance and
#  min.node.size = 5.

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_LA_corrected_10.png")
ggplot(varimp_mars) + theme_minimal() + labs(x="") #+ theme(panel.background = element_rect(fill = "white"))
ggsave(path.out)
```

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4044, 3685, 4032, 4044, 4044, 3696, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.2773324  0.6169393  0.2025296
#   2     extratrees  0.2692856  0.6437281  0.1982852
#   4     variance    0.2836790  0.5992575  0.2060827
#   4     extratrees  0.2717096  0.6339425  0.2004439
#   6     variance    0.2899917  0.5806674  0.2100017
#   6     extratrees  0.2755481  0.6223759  0.2037709
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees
#  and min.node.size = 5.

>>>>

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4718, 4690, 5040, 4718, 5055, 4704, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.1877289  0.7762104  0.1222690
#   2     extratrees  0.1945882  0.7537303  0.1274455
#   4     variance    0.1899769  0.7754308  0.1253349
#   4     extratrees  0.1925299  0.7604062  0.1270665
#   6     variance    0.1926697  0.7707287  0.1277624
#   6     extratrees  0.1930151  0.7601929  0.1280934
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = variance and min.node.size = 5.

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_LA_corrected_10.png")
ggplot(varimp_mars) + theme_minimal() + labs(x="") #+ theme(panel.background = element_rect(fill = "white"))
ggsave(path.out)

path.out <- paste0(path, "/outputs/rf/figures/varimp_LA_corrected_10.csv")
varimp_mars$importance %>% 
  rownames_to_column() %>%
  rename(variable = rowname,
         importance = Overall) %>% 
  write_csv(path.out)
```

@@

# [reproducible results]
# Random Forest 
# 
# 4862 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 4044, 3685, 4032, 4044, 4044, 3696, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE       Rsquared   MAE      
#   2     variance    0.2773784  0.6171406  0.2025901
#   2     extratrees  0.2696423  0.6424804  0.1985126
#   4     variance    0.2834811  0.5991036  0.2058774
#   4     extratrees  0.2720828  0.6324695  0.2007287
#   6     variance    0.2902072  0.5801010  0.2101899
#   6     extratrees  0.2755322  0.6215775  0.2037045
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees and min.node.size = 5.
